Adaptative Computation:\\ An Essay in Memory of John H. Holland

### 2016-02-25 paper.tex
addressed axelrod comment about mode consistency with env

Although the idea of default hierarchies was prevalent in knowledge
representation systems of the era, Holland made two key contributions.
The first was his emphasis on homomorphisms as a formal way to
evaluate model validity, an idea that dates back to Ross Ashby's
\emph{An Introduction to Cybernetics} \cite{Ashby1956}. Holland's
student Bernard Ziegler developed this idea into a formal theory of
computer modeling and simulation \cite{Ziegler1976}.  Even today,
these early homomorphic theories of modeling stand as the most elegant
approach we know of to characterize when a model is consistent with
the environment and how an intelligent agent, human or artificial, can
update a model to better reflect reality.

>>>>

Although the idea of default hierarchies was prevalent in knowledge
representation systems of the era, Holland made two key contributions.
The first was his emphasis on homomorphisms as a formal way to
evaluate model validity, an idea that dates back to Ross Ashby's
\emph{An Introduction to Cybernetics} \cite{Ashby1956}. Holland's
student Bernard Ziegler developed this idea into a formal theory of
computer modeling and simulation \cite{Ziegler1976}.  Even today,
these early homomorphic theories of modeling stand as the most elegant
approach we know of to characterize how consistent a model is with
the environment and how an intelligent agent, human or artificial, can
update a model to better reflect reality.
